Semantic Novelty Detection with Graphical Models on Dora Architecture

### 2011-05-04 semantic-nd/article.tex
More ideas organization

>>>>

\subsection{Graphical Models}

\section{Novelty Detection Threshold}
Novelty detection deals with the detection of data comming from a new class,
that the system is not aware during training.

It is often implemented around a.

When the data is all 
In such cases the detection threshold can be seen as a function responsible to order
the input space in such a way that .

When dealing with exact

\subsection{Conditional Density Probability}

\subsection{Optimal Novelty Detector using Unconditional Probability}
